---
title: "wk7-prac"
author: "Leandra"
date: "11/23/2021"
output: 
  html_document:
    toc: true
---

```{r message=FALSE}
library(tidyverse)
library(tmap)
library(geojsonio)
library(plotly)
library(rgdal)
library(sf)
library(sp)
library(spdep)
library(janitor)
library(here)
library(broom)
library(tidypredict)
library(car)
library(corrr)
library(ggcorrplot)
library(spatialreg)
library(spgwr)
```

## Load Data
```{r read data}
Londonwards <- st_read(here("../wk1",
               "statistical-gis-boundaries-london", 
               "ESRI", "London_Ward_CityMerged.shp"))

# qtm(Londonwards)

# specify some likely 'n/a' values
# also specify Latin1 as encoding as there is a pound sign (£) in one of the column headers
LondonWardProfiles <- read_csv("https://data.london.gov.uk/download/ward-profiles-and-atlas/772d2d64-e8c6-46cb-86f9-e52b4c7851bc/ward-profiles-excel-version.csv", 
                               na = c("", "NA", "n/a"), 
                               locale = locale(encoding = 'latin1'), 
                               col_names = TRUE)

# check all of the columns have been read in correctly
Datatypelist <- LondonWardProfiles %>% 
  summarise_all(class) %>%
  pivot_longer(everything(), 
               names_to="All_variables", 
               values_to="Variable_class")
# Datatypelist
```

```{r join boundaries and attributes}
# merge boundaries and data
LonWardProfiles <- Londonwards %>%
  left_join(.,
            LondonWardProfiles, 
            by = c("GSS_CODE" = "New code"))

# let's map our dependent variable to see if the join has worked:
tmap_mode("plot")
qtm(LonWardProfiles, 
    fill = "Average GCSE capped point scores - 2014", 
    borders = NULL,  
    fill.palette = "Blues")
```

```{r sec school data}
london_schools <- read_csv("https://data.london.gov.uk/download/london-schools-atlas/57046151-39a0-45d9-8dc0-27ea7fd02de8/all_schools_xy_2016.csv")

# from the coordinate values stored in the x and y columns, which look like they are latitude and longitude values, create a new points dataset
lon_schools_sf <- st_as_sf(london_schools, 
                           coords = c("x","y"), 
                           crs = 4326)

lond_sec_schools_sf <- lon_schools_sf %>%
  filter(PHASE=="Secondary")

tm_shape(Londonwards) + 
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(lond_sec_schools_sf) +
  tm_dots(col = "blue")
```

## Linear Regression
```{r linear regression}
# scatter plot
q <- qplot(x = `Unauthorised Absence in All Schools (%) - 2013`, 
           y = `Average GCSE capped point scores - 2014`, 
           data = LonWardProfiles)

# plot with a regression line
q + stat_smooth(method="lm", se=FALSE, size=1)
# + geom_jitter() 
# moves the points so they are not all on top of each other
# in actual fact it is incorrect (should not move points)

LonWardProfiles <- LonWardProfiles %>%
  clean_names()

# run the linear regression model and store its outputs in an object called model1
Regressiondata <- LonWardProfiles%>%
  dplyr::select(average_gcse_capped_point_scores_2014, 
                unauthorised_absence_in_all_schools_percent_2013)

model1 <- Regressiondata %>%
  lm(average_gcse_capped_point_scores_2014 ~
       unauthorised_absence_in_all_schools_percent_2013,
     data = .)

summary(model1)
tidy(model1)
glance(model1)
# from the broom package

# see the predictions for each point
# Regressiondata %>%
#   tidypredict_to_column(model1)
```

## Assumptions of Linear Regression
### Assumption 1: Linear relationship between x and y
First check the distribution of our variables. If the variables are normally distributed, then there is a good chance that if the two variables are in some way correlated, this will be a linear relationship.
```{r linear relationship between x and y}
# basic histogram of counts
# ggplot(LonWardProfiles, aes(x=average_gcse_capped_point_scores_2014)) + 
#   geom_histogram(binwidth = 5)
  
ggplot(LonWardProfiles, aes(x=average_gcse_capped_point_scores_2014)) + 
  geom_histogram(aes(y = ..density..), 
                 # use density so that we can overlay the smoothed density estimate
                 binwidth = 5) + 
  geom_density(colour="red", 
               size=1, 
               adjust=1)

ggplot(LonWardProfiles, 
       aes(x = unauthorised_absence_in_all_schools_percent_2013)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = 0.1) + 
  geom_density(colour="red",
               size=1, 
               adjust=1)
```

```{r transforming skewed data}
ggplot(LonWardProfiles, aes(x=median_house_price_2014)) + 
  geom_histogram()

qplot(x = median_house_price_2014, 
      y = average_gcse_capped_point_scores_2014, 
      data = LonWardProfiles)

# log transformation
ggplot(LonWardProfiles, aes(x=log(median_house_price_2014))) + 
  geom_histogram()

# symbox function from car package
# look for the most normal distribution
# -1 here is the only power that doesn't have any outliers
symbox(~median_house_price_2014, 
       LonWardProfiles, 
       na.rm = T,
       powers = seq(-3, 3, by = .5))

ggplot(LonWardProfiles, aes(x=(median_house_price_2014)^-1)) + 
  geom_histogram()

qplot(x = (median_house_price_2014)^-1, 
      y = average_gcse_capped_point_scores_2014,
      data = LonWardProfiles)

qplot(x = log(median_house_price_2014), 
      y = average_gcse_capped_point_scores_2014, 
      data = LonWardProfiles)

# be careful about interpreting models after transforming the variables
# https://data.library.virginia.edu/interpreting-log-transformations-in-a-linear-model/
```
### Assumption 2: Normally distributed residuals
```{r normally distributed residuals}
# save the residuals into your dataframe
model_data <- model1 %>%
  augment(., Regressiondata)

# plot residuals
qplot(x = .resid, 
      data = model_data,
      main = "Distribution of residuals",
      xlab = "residuals", 
      ylab = "count") +
  geom_histogram()
```

### Assumption 3: No multicollinearity in independent variables
```{r check for multicollinearity}
# add another variable (house price) into the model
Regressiondata2 <- LonWardProfiles %>%
  dplyr::select(average_gcse_capped_point_scores_2014,
                unauthorised_absence_in_all_schools_percent_2013,
                median_house_price_2014)

model2 <- lm(average_gcse_capped_point_scores_2014 ~ unauthorised_absence_in_all_schools_percent_2013 + 
               I(median_house_price_2014^-1), 
             data = Regressiondata2)

#show the summary of those outputs
tidy(model2)
glance(model2)

# and for future use, write the residuals out
model_data2 <- model2 %>%
  augment(., Regressiondata2)

# also add them to the shapelayer
LonWardProfiles <- LonWardProfiles %>%
  mutate(model2resids = residuals(model2))

Correlation <- LonWardProfiles %>%
  st_drop_geometry() %>%
  dplyr::select(average_gcse_capped_point_scores_2014,
                unauthorised_absence_in_all_schools_percent_2013,
                median_house_price_2014) %>%
  mutate(transformed_house_price = I(median_house_price_2014^-1)) %>%
  rename(., 
         unauthorised_absence = unauthorised_absence_in_all_schools_percent_2013) %>%
  correlate() %>%
  # just focus on unauthorised absence and house prices
  # remove the dependent variable
  focus(-average_gcse_capped_point_scores_2014, 
        -median_house_price_2014,
        mirror = TRUE)

Correlation <- Correlation %>% 
  column_to_rownames(., var = "term")

# corr_matrix <- data.matrix(Correlation)

# visualise the correlation matrix
ggcorrplot(Correlation, type = "lower")

# correlation matrix with more variables
Correlation_all <- LonWardProfiles %>%
  st_drop_geometry() %>%
  dplyr::select(c(10:74)) %>%
  correlate()

rplot(Correlation_all)

# another way is to check VIF
vif(model2)
```

### Assumption 4: Homoscedasticity
Equal variance
```{r homoscedasticity}
# print some model diagnostics
par(mar=c(1,1,1,1))
par(mfrow=c(2,2)) #plot to 2 by 2 array
plot(model2)
par(mfrow=c(1,1)) #change back

```

### Assumption 5: Independent residuals
For non-spatial data, we can use the Durbin-Watson test.

For spatial data, the residuals should not have spatial autocorrelation. Last week we looked for spatial clustering using Moran's I etc. -- those are measures of spatial autocorrelation.

```{r map the residuals}
# run durbin-watson test
# DW <- durbinWatsonTest(model2)
# tidy(DW)

# map the residuals and look for obvious patterns
# e.g. some blue areas next to other blue areas and some red/orange areas next to other red/orange areas
# see tmaptools::palette_explorer() for the named palettes
# qtm(LonWardProfiles, fill = "model2resids", fill.palette="PiYG")

tmap_mode("view")
tm_shape(LonWardProfiles) +
  tm_polygons("model2resids",
              palette = "RdYlBu") +
  tm_shape(lond_sec_schools_sf) + 
  tm_dots(col = "TYPE")
```

```{r Morans I}
# preparation for Moran's I
# calculate the centroids of all Wards in London
coordsW <- LonWardProfiles %>%
  st_centroid() %>%
  st_geometry()

# plot(coordsW)

# the poly2nb function builds a neighbours list based on regions with contiguous boundaries, that is sharing one or more boundary point
# queen = TRUE means a single shared boundary point meets the contiguity condition
LWard_nb <- LonWardProfiles %>%
  poly2nb(., queen=T)
# summary(LWard_nb)

plot(LWard_nb, st_geometry(coordsW), col="red")
plot(LonWardProfiles$geometry, add = T)

# knearneigh returns a matrix with the indices of points belonging to the set of the k nearest neighbours of each other
knn_wards <- coordsW %>%
  knearneigh(., k=4)
# convert the knn object returned by knearneigh into a neighbours list
LWard_knn <- knn_wards %>%
  knn2nb()

plot(LWard_knn, st_geometry(coordsW), col="blue")
plot(LonWardProfiles$geometry, add = T)

# add spatial weights to neighbours list
Lward.queens_weight <- LWard_nb %>%
  nb2listw(., style="C")
# C is globally standardised (sums over all links to n)
# B is the basic binary coding
# W is row standardised (sums over all links to n), 

Lward.knn_4_weight <- LWard_knn %>%
  nb2listw(., style="C")

# run Moran's I test for spatial autocorrelation
Queen <- moran.test(LonWardProfiles$model2resids, 
                    Lward.queens_weight) %>%
  tidy()

# Queen

Nearest_neighbour <- moran.test(LonWardProfiles$model2resids,
                                Lward.knn_4_weight) %>%
  tidy()

# Nearest_neighbour
```
We can see that the Moran’s I statistic is somewhere between 0.26 and 0.29. Remembering that Moran’s I ranges from between -1 and +1 (0 indicating no spatial autocorrelation) we can conclude that there is some weak to moderate spatial autocorrelation in our residuals. 

How to deal with this?

* Spatially lagged regression model
* Spatial error model

## Spatially lagged regression model
The model incorporates spatial dependence explicitly by adding a “spatially lagged” dependent variable y on the right-hand side of the regression equation. 

Decomposes the error term into a spatially lagged term for the dependent variable (which is correlated with the dependent variable) and an independent error term.

Rho is our spatial lag that measures the variable in the surrounding spatial areas as defined by the spatial weights matrix. We use this as an extra explanatory variable to account for clustering (identified by Moran’s I).

```{r spatial lag model}
# original Model
# model2 <- lm(average_gcse_capped_point_scores_2014 ~
#                unauthorised_absence_in_all_schools_percent_2013 +
#                I(median_house_price_2014^-1),
#              data = Regressiondata2)
# 
# tidy(model2)

# run the spatially-lagged regression model with the spatial weights matrix from earlier
# Spatial simultaneous autoregressive lag model estimation
# raising house price to the power of -1 causes an error, so use log transformation instead
splag_model <- lagsarlm(average_gcse_capped_point_scores_2014 ~
                          unauthorised_absence_in_all_schools_percent_2013 +
                          log(median_house_price_2014), 
                        data = Regressiondata2, 
                        Lward.queens_weight)

# what do the outputs show?
tidy(splag_model)
# results show that rho is statistically insignificant
# there is an insignificant and small effect associated with the spatially lagged dependent variable

# model stats
glance(splag_model)

t <- summary(splag_model)

# now use knn to run a spatially-lagged regression model
splag_model_knn4 <- lagsarlm(average_gcse_capped_point_scores_2014 ~
                               unauthorised_absence_in_all_schools_percent_2013 +
                               log(median_house_price_2014), 
                             data = Regressiondata2,
                             Lward.knn_4_weight)

# what do the outputs show?
tidy(splag_model_knn4)
# results are significant

# check that the residuals from the spatially lagged model are now no-longer exhibiting spatial autocorrelation
# write out the residuals
LonWardProfiles <- LonWardProfiles %>%
  mutate(splag_model_knn_resids = residuals(splag_model_knn4))

KNN4Moran <- moran.test(LonWardProfiles$splag_model_knn_resids, 
                        Lward.knn_4_weight) %>% 
  tidy()

KNN4Moran
# Moran’s I is close to 0 indicating no spatial autocorrelation in our residuals.
```

## Spatial error model
The spatial error model treats spatial correlation primarily as a nuisance and focuses on estimating the parameters for the independent variables of interest and essentially disregards the possibility that the observed correlation may reflect something meaningful about the data generation process.

```{r spatial error model}
# Spatial simultaneous autoregressive error model estimation
sem_model <- errorsarlm(average_gcse_capped_point_scores_2014 ~ unauthorised_absence_in_all_schools_percent_2013 + 
                           log(median_house_price_2014), 
                         data = Regressiondata2,
                         Lward.knn_4_weight)

tidy(sem_model)
```

## Lagrange Multiplier Test
This test can help us decide whether to use the lag model or error model. 
This test expects row standardisation.
```{r lagrange multiplier test}
Lward.queens_weight_ROW <- LWard_nb %>%
  nb2listw(., style="W")

lm.LMtests(model2, Lward.queens_weight_ROW, 
           test = c("LMerr","LMlag","RLMerr","RLMlag","SARMA"))

```

## Dummy variables
```{r dummy variables}
extradata <- read_csv("https://www.dropbox.com/s/qay9q1jwpffxcqj/LondonAdditionalDataFixed.csv?raw=1")

# add the extra data too
LonWardProfiles <- LonWardProfiles %>%
  left_join(., 
            extradata, 
            by = c("gss_code" = "Wardcode")) %>%
  clean_names()

# print some of the column names
LonWardProfiles %>%
  names() %>%
  tail(., n=10)

p <- ggplot(LonWardProfiles, 
            aes(x = unauth_absence_schools11, 
                y = average_gcse_capped_point_scores_2014))
p + geom_point(aes(colour = inner_outer)) 

# first, let's make sure R is reading our inner_outer variable as a factor
# see what it is at the moment...
# isitfactor <- LonWardProfiles %>%
#   dplyr::select(inner_outer) %>%
#   summarise_all(class)
# 
# isitfactor

typeof(LonWardProfiles$inner_outer)

# change to factor (aka categorical data)
LonWardProfiles <- LonWardProfiles %>%
  mutate(inner_outer = as.factor(inner_outer))

# now run the model
model3 <- lm(average_gcse_capped_point_scores_2014 ~ unauthorised_absence_in_all_schools_percent_2013 + 
               log(median_house_price_2014) + 
               inner_outer, 
             data = LonWardProfiles)

tidy(model3)

# check which is our reference group
contrasts(LonWardProfiles$inner_outer)

# change reference group if needed
# LonWardProfiles <- LonWardProfiles %>%
#   mutate(inner_outer = relevel(inner_outer, 
#                                ref="Outer"))
# 
# model3 <- lm(average_gcse_capped_point_scores_2014 ~ unauthorised_absence_in_all_schools_percent_2013 + 
#                log(median_house_price_2014) + 
#                inner_outer, 
#              data = LonWardProfiles)
# 
# tidy(model3)
```

## Geographically Weighted Regression
The basic idea behind GWR is to explore how the relationship between a dependent variable (Y) and one or more independent variables (the Xs) might vary geographically.  

**Spatial nonstationarity** refers to variations in the relationship between an outcome variable and a set of predictor variables across space.  

Instead of assuming that a single model can be fitted to the entire study region, it looks for geographical differences.  

Apply this when you think there is some local variation that is not captured in the global model.  

GWR operates by moving a search window from one regression point to the next, working sequentially through all the existing regression points in the dataset.  
For a data set of 150 observations GWR will fit 150 weighted regression models.  
[GWR tutorial](https://gdsl-ul.github.io/san/geographically-weighted-regression)  

What area should the search window cover each time?

* geographic distance
    + fixed bandwidth

* k nearest neighbour
    + by fixing the number of neighbours, we vary the search area from point to point
    + this is called adaptive bandwidth (search window size)
    
```{r final OLS linear regression model}
# select some variables from the data file
myvars <- LonWardProfiles %>%
  dplyr::select(average_gcse_capped_point_scores_2014,
                unauthorised_absence_in_all_schools_percent_2013,
                median_house_price_2014,
                rate_of_job_seekers_allowance_jsa_claimants_2015,
                percent_with_level_4_qualifications_and_above_2011,
                inner_outer)

# check their correlations are OK
# pearson correlation is only appropriate for interval or ratio data
# we are only concerned about multicollinearity between predictor variables
Correlation_myvars <- myvars %>%
  st_drop_geometry() %>%
  mutate(transformed_house_price = log(median_house_price_2014)) %>%
  dplyr::select(-inner_outer, 
                -average_gcse_capped_point_scores_2014, 
                -median_house_price_2014) %>%
  rename(., 
         unauthorised_absence = unauthorised_absence_in_all_schools_percent_2013,
         percent_qualified = percent_with_level_4_qualifications_and_above_2011,
         jsa_claimants_rate = rate_of_job_seekers_allowance_jsa_claimants_2015)

# get correlation matrix
cormat <- cor(Correlation_myvars, use="complete.obs", method="pearson")

# significance test
sig1 <- corrplot::cor.mtest(Correlation_myvars, conf.level = .95)

# create a correlogram
corrplot::corrplot(cormat, type="lower",
                   method = "circle", 
                   order = "original", 
                   tl.cex = 0.7,
                   p.mat = sig1$p, sig.level = .05, 
                   col = viridis::viridis(100, option = "plasma"),
                   diag = FALSE)
# looks like percent_qualified and transformed_house_price are quite highly correlated
# the size of the circle reflects the strength of the relationships as captured by the Pearson correlation coefficient 
# crosses indicate statistically insignificant relationships at the 95% level of confidence

# pairs(Correlation_myvars)

final_eq <- average_gcse_capped_point_scores_2014 ~ 
  unauthorised_absence_in_all_schools_percent_2013 + 
  log(median_house_price_2014) +
  inner_outer +
  rate_of_job_seekers_allowance_jsa_claimants_2015 +
  percent_with_level_4_qualifications_and_above_2011

# run a final OLS model
model_final <- lm(final_eq, 
                  data = myvars)

tidy(model_final)

vif(model_final)
# The VIFs are below 10 indicating that multicollinearity is not highly problematic.

LonWardProfiles <- LonWardProfiles %>%
  mutate(model_final_res = residuals(model_final))

par(mfrow=c(2,2))
plot(model_final)

qtm(LonWardProfiles, fill = "model_final_res")

final_model_Moran <- moran.test(LonWardProfiles$model_final_res,
                                Lward.knn_4_weight) %>%
  tidy()

final_model_Moran
```

### Search for optimal kernel bandwidth
```{r get coordinates of centroids}
coordsW2 <- st_coordinates(coordsW)

LonWardProfiles2 <- cbind(LonWardProfiles, coordsW2)
```

```{r select bandwidth}
# find optimal kernel bandwidth
GWR_bandwidth <- gwr.sel(final_eq,
                        data = LonWardProfiles2, 
                        coords = cbind(LonWardProfiles2$X, LonWardProfiles2$Y),
                        # provide an adaptive bandwidth as opposed to a fixed bandwidth
                        adapt = TRUE)
# adapt = TRUE: find the proportion between 0 and 1 of observations to include in weighting scheme (k-nearest neighbours)
# adapt = FALSE: find global bandwidth

GWR_bandwidth
# The optimal bandwidth is about 0.016 meaning 1.6% of all the total spatial units should be used for the local regression based on k-nearest neighbours. This is about 10 of the 626 wards.
```
### Fit GWR model
```{r gwr model}
# fit the gwr model based on adaptive bandwidth
gwr_abw = gwr(final_eq, 
                data = LonWardProfiles2, 
                coords = cbind(LonWardProfiles2$X, LonWardProfiles2$Y), 
                adapt = GWR_bandwidth, 
                # matrix output
                hatmatrix = TRUE, 
                # standard error
                se.fit = TRUE)

# print the results of the model
gwr_abw

results <- as.data.frame(gwr_abw$SDF)
names(results)

# save localR2 and coefficients to original data frame
LonWardProfiles2$abw_localR2 <- results$localR2

LonWardProfiles2$coef_unauth_abs <- results$unauthorised_absence_in_all_schools_percent_2013

LonWardProfiles2$coef_house_price <- results$log.median_house_price_2014.

LonWardProfiles2$coef_inner <- results$inner_outerInner 
# check reference category -- inner is 1, outer is 0

LonWardProfiles2$coef_jsa <- results$rate_of_job_seekers_allowance_jsa_claimants_2015

LonWardProfiles2$coef_lvl4qual <- results$percent_with_level_4_qualifications_and_above_2011

# map local R2
tmap_mode("plot")

legend_title = expression("Adaptive bandwidth: Local R2")

map_abgwr1 = tm_shape(LonWardProfiles2) +
  tm_fill(col = "abw_localR2", title = legend_title, 
          palette = "magma", style = "cont") +
  tm_borders(col = "white", lwd = .1) + 
  tm_compass(type = "arrow", position = c("right", "top") , size = 5) + 
  tm_scale_bar(breaks = c(0,1,2), text.size = 0.7, position =  c("center", "bottom")) +
  tm_layout(bg.color = "white")

map_abgwr1

# simple way to plot coefficients
# tm_shape(LonWardProfiles2) +
#   tm_polygons(col = "coef_unauth_abs", 
#               palette = "RdBu", 
#               alpha = 0.5)

# nicer maps
# use tmaptools::palette_explorer() to choose palette

# unauthorised_absence_in_all_schools_percent_2013
legend_title = expression("Unauthorised absence")

map_abgwr2 = tm_shape(LonWardProfiles2) +
  tm_fill(col = "coef_unauth_abs", title = legend_title, 
          palette = "RdBu", style = "cont") + 
  tm_borders(col = "white", lwd = .1)  +
  tm_compass(type = "arrow", position = c("right", "top") , size = 5) +
  tm_scale_bar(breaks = c(0,1,2), text.size = 0.7, position =  c("center", "bottom")) + 
  tm_layout(bg.color = "white")

# log(median_house_price)
legend_title = expression("Log of median house price")

map_abgwr3 = tm_shape(LonWardProfiles2) +
  tm_fill(col = "coef_house_price", title = legend_title, 
          palette = "RdBu", style = "cont") + 
  tm_borders(col = "white", lwd = .1)  + 
  tm_scale_bar(breaks = c(0,1,2), text.size = 0.7, position =  c("center", "bottom")) + 
  tm_layout(bg.color = "white") 

tmap_arrange(map_abgwr2, map_abgwr3)
```

### Assessing statistical significance
Roughly, if a coefficient estimate has an absolute value of t greater than 1.96 and the sample is sufficiently large, then it is statistically significant.
```{r statistical significance}
# compute t statistic
LonWardProfiles2$t_unauth_abs = results$unauthorised_absence_in_all_schools_percent_2013 / results$unauthorised_absence_in_all_schools_percent_2013_se

# categorise t values
LonWardProfiles2$t_unauth_abs_cat <- cut(LonWardProfiles2$t_unauth_abs,
                     breaks = c(min(LonWardProfiles2$t_unauth_abs), 
                              -1.96, 1.96, 
                              max(LonWardProfiles2$t_unauth_abs)),
                     labels = c("sig","nonsig", "sig"))

# map statistically significant coefs for unauthorised absence
legend_title = expression("Unauthorised absence: significant")

map_sig = tm_shape(LonWardProfiles2) + 
  tm_fill(col = "t_unauth_abs_cat", title = legend_title, 
          legend.hist = TRUE, midpoint = NA, 
          textNA = "", colorNA = "white") +  
  tm_borders(col = "white", lwd = .1)  + 
  tm_compass(type = "arrow", position = c("right", "top") , size = 5) + 
  tm_scale_bar(breaks = c(0,1,2), text.size = 0.7, position =  c("center", "bottom")) + 
  tm_layout(bg.color = "white", legend.outside = TRUE)

map_sig
# repeat for other variables

# run the significance test
# sigTest = abs(results$log.median_house_price_2014.) - 
#   2 * results$log.median_house_price_2014._se
# 
# # store significance results
# LonWardProfiles2 <- LonWardProfiles2 %>%
#   mutate(GWRHousePriceSig = sigTest)
# 
# tm_shape(LonWardProfiles2) +
#   tm_polygons(col = "GWRHousePriceSig",
#               palette = "RdYlBu")
```

